On particular examples of planar integral point sets and their classification \footnote{ This work was carried out at Voronezh State University and supported by the Russian Science Foundation grant 19-11-00197. }

### 2021-02-24 AvdMomZvolA_examples/ips_examples.tex
8ки которые не могут быть вместе
Пробелы и переносы
Системы с 2мя осями симметрии

\item
$\mathcal{P_42}=\sqrt{154}/{1} * \{ (\pm 345596160; 0);
(\pm219513840 -15069600);
(\pm260201760; 0);
(\pm225792840; 0);
(\pm213234840; 0);
(\pm153961080; 0);
(\pm144668160; 0
(\pm25116000; 0);
(\pm694026840; 0);
(\pm514710560; 0);
(\pm359116940; 0);
(\pm13423904; 0);
(\pm75682880; 0);
(\pm464143680; 0);
(\pm827069880; 0);
(\pm92144325; 0);
(\pm1195180740; 0);
(\pm1236558752; 0);
(\pm44590560; 0);
(\pm339925740; 0);
(\pm117312468; 0)\}
$
(Figure~\ref{42_symm.png}),

@@

\item
$\mathcal{P_46}=\sqrt{154}/{1} * \{ (\pm435751680; 0);
(\pm276778320; -19000800);
(\pm328080480; 0);
(\pm284695320; 0);
(\pm268861320; 0);
(\pm194124840; 0);
(\pm182407680; 0);
(\pm31668000; 0);
(\pm1559139296; 0);
(\pm1506967020; 0);
(\pm1042827240; 0);
(\pm875077320; 0);
(\pm648982880; 0);
(\pm585224640; 0);
(\pm452799620; 0);
(\pm95426240; 0);
(\pm16925792; 0);
(\pm116181975; 0);
(\pm428602020; 0);
(\pm56222880; 0);
(\pm769560480; 0);
(\pm626458560; 0);
(\pm130761918; 0)\}
$
(Figure~\ref{46_symm.png}),

@@

\item
$\mathcal{P_48}=\sqrt{154}/{1} * \{ (\pm10022288640; 0);
( \pm6365901360 ; -437018400);
( \pm7545851040 ; 0);
( \pm6547992360 ; 0);
( \pm6183810360 ; 0);
( \pm4464871320 ; 0);
( \pm4195376640 ; 0);
( \pm728364000 ; 0);
( \pm35860203808 ; 0);
( \pm34660241460 ; 0);
( \pm23985026520 ; 0);
( \pm20126778360 ; 0);
( \pm14926606240 ; 0);
( \pm13460166720 ; 0);
( \pm10414391260 ; 0);
( \pm2194803520 ; 0);
( \pm389293216 ; 0);
( \pm2672185425 ; 0);
( \pm9857846460 ; 0);
( \pm1293126240 ; 0);
( \pm17699891040 ; 0);
( \pm14408546880 ; 0);
( \pm3007524114 ; 0);
( \pm3402061572 ; 0)\}
$
(Figure~\ref{48_symm.png}),

@@

TODO: specify the irrational distance:

Note that distance between the non-adoptable points is
\begin{equation}
	\sqrt{\left(\frac{}{} - \frac{}{}\right)^2 + \left(\frac{}{} - \frac{}{}\right)^2}
\end{equation}

@@

TODO: 11\_14450\_1\_8693fad981c82dc92d7c9365bcb9945e

@@

TODO: 8\_2535\_1\_d680ff2d172ebe40250a54ca9419af34

>>>>

\item
$\mathcal{P_42}=\sqrt{154}/{1} * \{
(\pm 345596160; 0);
(\pm219513840 -15069600);
(\pm260201760; 0);\\
(\pm225792840; 0);
(\pm213234840; 0);
(\pm153961080; 0);
(\pm144668160; 0);
(\pm25116000; 0);\\
(\pm694026840; 0);
(\pm514710560; 0);
(\pm359116940; 0);
(\pm13423904; 0);
(\pm75682880; 0);\\
(\pm464143680; 0);
(\pm827069880; 0);
(\pm92144325; 0);
(\pm1195180740; 0);
(\pm1236558752; 0);\\
(\pm44590560; 0);
(\pm339925740; 0);
(\pm117312468; 0)\}
$
(Figure~\ref{42_symm.png}),

@@

\item
$\mathcal{P_46}=\sqrt{154}/{1} * \{
(\pm435751680; 0);
(\pm276778320; -19000800);
(\pm328080480; 0);
(\pm284695320; 0);\\
(\pm268861320; 0);
(\pm194124840; 0);
(\pm182407680; 0);
(\pm31668000; 0);
(\pm1559139296; 0);\\
(\pm1506967020; 0);
(\pm1042827240; 0);
(\pm875077320; 0);
(\pm648982880; 0);
(\pm585224640; 0);\\
(\pm452799620; 0);
(\pm95426240; 0);
(\pm16925792; 0);
(\pm116181975; 0);
(\pm428602020; 0);\\
(\pm56222880; 0);
(\pm769560480; 0);
(\pm626458560; 0);
(\pm130761918; 0)\}
$
(Figure~\ref{46_symm.png}),

@@

\item
$\mathcal{P_48}=\sqrt{154}/{1} * \{
( \pm10022288640; 0);
( \pm6365901360 ; -437018400);
( \pm7545851040 ; 0);\\
( \pm6547992360 ; 0);
( \pm6183810360 ; 0);
( \pm4464871320 ; 0);
( \pm4195376640 ; 0);
( \pm728364000 ; 0);\\
( \pm35860203808 ; 0);
( \pm34660241460 ; 0);
( \pm23985026520 ; 0);
( \pm20126778360 ; 0);\\
( \pm14926606240 ; 0);
( \pm13460166720 ; 0);
( \pm10414391260 ; 0);
( \pm2194803520 ; 0);
( \pm389293216 ; 0);\\
( \pm2672185425 ; 0);
( \pm9857846460 ; 0);
( \pm1293126240 ; 0);
( \pm17699891040 ; 0);
( \pm14408546880 ; 0);\\
( \pm3007524114 ; 0);
( \pm3402061572 ; 0)\}
$
(Figure~\ref{48_symm.png}),

@@

\begin{figure}[h!]
	\begin{minipage}[h]{0.32\linewidth}
		\begin{center}
			\includegraphics[width=1\linewidth]{./img/8_2520_143_symm1.png}\\ a)
		\end{center}
	\end{minipage}
	\hfill
	\begin{minipage}[h]{0.32\linewidth}
		\begin{center}
			\includegraphics[width=1\linewidth]{./img/8_2520_143_symm2.png}\\ b)
		\end{center}
	\end{minipage}
	\begin{minipage}[h]{0.32\linewidth}
		\begin{center}
			\includegraphics[width=1\linewidth]{./img/8_2520_143_4a27_other.png}\\ c)
		\end{center}
	\end{minipage}
	\hfill
	\caption{IPSs with cardinality 8 and diameter 2520 with many common points}
	\label{8_with_many_common}
\end{figure}

\begin{itemize}
\item
$\mathcal{P}=\sqrt{143}/2*\{
( \pm1620 ; 0);
( \pm1920 ; 300);
( \pm735 ; 75);
( \pm340 ; 0);
\}$

\item
$\mathcal{P}=\sqrt{143}/2*\{
( \pm1620 ; 0);
( \pm1920 ; 300);
( \pm735 ; 75);
( \pm1767 ; 147);
\}$

\item
$\mathcal{P}=
\sqrt{143}/2*\{
( \pm1620 ; 0);
( \pm1920 ; 300);
( \pm735 ; 75);
( -340 ; 0);
( 1767 ; 147);
\}$

\end{itemize}
TODO: specify the irrational distance:

Note that distance between the non-adoptable points is
\begin{equation}
	\sqrt{\left(\frac{1767}{2} - \frac{340}{2}\right)^2 + \left(\frac{147}{2}\right)^2\cdot143} = 2\sqrt{320401}
\end{equation}

Where 320401 is prime.

@@

\begin{figure}[h!]
center{\includegraphics[width=1\linewidth]{./img/15_61960444_1_other.png}}
\parbox{1\linewidth}{\caption{IPS of cardinality 15 and diameter 61960444}
\label{15_61960444_1.png}}
\end{figure}

\begin{figure}[h!]
center{\includegraphics[width=1\linewidth]{./img/15_45970652_1_other.png}}
\parbox{1\linewidth}{\caption{IPS of cardinality 15 and diameter 45970652}
\label{15_45970652_1.png}}
\end{figure}

\begin{itemize}
\item
$\mathcal{P}=\sqrt{1}/1*\{
( \pm9406950 ; 0);
( \pm7063350 ; 0);
( 2962050 ; \pm3437280);
( 0 ; 0);
( -2962050 ; \pm3437280);\\
( \pm2188662 ; 0);
( \pm30980222 ; 0);
( \pm2914854 ; 0);
\}$

\item
$\mathcal{P}=\sqrt{1}/1*\{
( \pm6979350 ; 0);
( \pm5240550 ; 0);
( 2197650 ; \pm2550240);
( 0 ; 0);
( -2197650 ; \pm2550240);\\
( \pm1623846 ; 0);
( \pm22985326 ; 0);
( \pm2476152 ; 0);
\}$
\end{itemize}

%TODO:

%TODO: 11_14450_1_8693fad981c82dc92d7c9365bcb9945e

@@

%TODO: 8_2535_1_d680ff2d172ebe40250a54ca9419af34
